Authors Response to Reviewer's Comments

### 2023-10-10 manuscript/review/authorsResponse.qmd
more updates in the revision before sending to co-authors

Our main take-away from this manuscript is that while it would certainly be possible to calibrate all 15 models against the EuFoRIa data, it is important to ensure that this aligns with the study's goals. If the goal is to provide extrapolation into a future climate, calibrating against data under the current climate may not be reliable, as shown by the two models in our set that *were* calibrated against such data (i.e., SIBYLA and xComp). This is why we believe it is valuable to test the performance of the models "as they are", i.e. as we have done in this study.

@@

Our general comments to reviewer 1:

@@

[PENDING: I am going to do this.]{.underline}

@@

[Clean together with comment 2]{.underline}

@@

In this first assessment we were not aiming at identify what specific subcomponents may hold the key and therefore dased on the current approach we could not provide more concrete recommendation for model development which most likely be specific for each of the 15 models. Maybe we need more such studies, including calibration as a first step, and then application against a withheld part of the data; or application (and comparison) under climate change scenarios to evaluate the robustness of the signal under future conditions.

@@

### [COMMENT 13]{.underline}

@@

### **COMMENT 18**

@@

### **COMMENT 19**

@@

### [**COMMENT 20**]{.underline}

@@

Response to comment 22:

@@

### **COMMENT 23**

@@

### **COMMENT 24**

@@

### **COMMENT 26**

@@

Response to comment 26:

@@

### **COMMENT 27**

@@

Response to comment 27:

@@

### **COMMENT 28**

@@

Response to comment 28:

@@

### **COMMENT 29**

@@

Response to comment 29:

@@

### **COMMENT 30**

@@

Response to comment 30:

@@

### **COMMENT 31**

@@

Response to comment 31:

Please, see our reply on comment 25

### **COMMENT 32**

@@

Response to comment 32:

@@

### **COMMENT 33**

@@

Response to comment 33:

@@

### [**COMMENT 34**]{.underline}

@@

Response to comment 34:

@@

### **COMMENT 35**

@@

Response to comment 35:

@@

### **COMMENT 36**

@@

Response to comment 36:

@@

### **COMMENT 37**

@@

Response to comment 37:

@@

### **COMMENT 38**

@@

Response to comment 38:

@@

**COMMENT 39**

@@

Response to comment 39:

@@

### **COMMENT 40**

@@

Response to comment 40:

@@

### **COMMENT 41**

@@

### **COMMENT 42**

@@

### **COMMENT 43**

@@

### **COMMENT 44**

@@

Response to comment 44:

@@

### **COMMENT 45**

@@

Response to comment 45:

@@

### **COMMENT 46**

@@

Response to comment 46:

Following the reviewer's comment on the lack of clarity of the selected thresholds explanation we have changed at the beginning of the section simulation protocol the first sentence where we explain that we considered tree regeneration as the passing of a breast height diameter threshold of 7 and 10 cm. We have also reported later on in this section (but before this line) that each of the models reported the number of trees crossing the two diameter thresholds.

@@

Response to comment 47:

Following the reviewer recomendation we have changed the equation formulation to better represent the Reineke relationship. The reviewer is correct that the Reineke is applied to all stems in the stand, in our case the N value is only changing due to the available regeneration at the two diameter thresholds as the adult trees number is the same. By comparing our expected relationship of recruited trees at 7 and 10cm with the Reineke value we are just comparing to a theoretical value in fully stocked stands. We have use the coefficient -1.605 because Reineke attributed a general validity to this allometric coefficient for fully stocked, even-aged forest stands, regardless of tree species and site.

@@

Response to comment 50:

@@

Response to comment 51:

We have changed the text.

@@

@@

Response to comment 53:

@@

Response to comment 54:

@@

Response to comment 55:

@@

@@

### [COMMENT 57]{.underline}

@@

@@

[Should we add here:]{.underline}

["Using 15 models built to capture long-term forest dynamics at the stand, landscape, and global levels, we simulate tree regeneration at 200 sites representing large environmental gradients across Central Europe WITHOUT DISTURBANCES CONSIDERATION" ? or something like this?]{.underline}

@@

@@

Response to comment 62:

@@

Response to comment 63:

@@

@@

Response to comment 65:

### COMMENT 65

@@

Response to comment 65:

>>>>

Thank you for taking the time to review our manuscript and for your comments. Our main take-away from this manuscript is that while it would certainly be possible to calibrate all 15 models against the EuFoRIa data, it is important to ensure that this aligns with the study's goals. If the goal is to provide extrapolation into a future climate, calibrating against data under the current climate may not be reliable, as shown by the two models in our set that *were* calibrated against such data (i.e., SIBYLA and xComp). This is why we believe it is valuable to test the performance of the models "as they are", i.e. as we have done in this study.

@@

**Our general comments to reviewer 1:**

@@

[Pending]{.underline}

@@

[Clean together with comment 3]{.underline}

@@

In this first assessment we were not aiming at identify what specific subcomponents may hold the key and therefore based on the current approach we could not provide more concrete recommendation for model development which most likely be specific for each of the 15 models. Maybe we need more such studies, including calibration as a first step, and then application against a withheld part of the data; or application (and comparison) under climate change scenarios to evaluate the robustness of the signal under future conditions.

@@

@@

@@

@@

### [COMMENT 20]{.underline}

@@

@@

@@

@@

@@

@@

@@

**Response to comment 24:**

@@

@@

@@

@@

@@

### COMMENT 27

@@

**Response to comment 27:**

@@

### COMMENT 28

@@

**Response to comment 28:**

### COMMENT 29

@@

**Response to comment 32:**

@@

### COMMENT 30

@@

**Response to comment 30:**

@@

### COMMENT 31

@@

**Response to comment 31:**

@@

### COMMENT 32

@@

**Response to comment 32:**

@@

### COMMENT 33

@@

**Response to comment 33:**

@@

### COMMENT 34

@@

**Response to comment 34:**

@@

### COMMENT 35

@@

**Response to comment 35:**

@@

### COMMENT 36

@@

**Response to comment 36:**

@@

### **CO**MMENT 37

@@

**Response to comment 37:**

@@

### COMMENT 38

@@

### COMMENT 39

@@

### COMMENT 40

@@

### COMMENT 41

@@

@@

### COMMENT 42

@@

**Response to comment 42:**

@@

### COMMENT 43

@@

**Response to comment 43:**

Following the reviewer's comment on the lack of clarity of the selected thresholds explanation we have changed at the beginning of the section simulation protocol the first sentence where we explain that we considered tree regeneration as the passing of a breast height diameter threshold of 7 and 10 cm. We have also reported later on in this section (but before this line) that each of the models reported the number of trees crossing the two diameter thresholds. L\[XX-XX\]

### COMMENT 44

@@

**Response to comment 44:**

Following the reviewer recommendation we have changed the equation formulation to better represent the Reineke relationship. The reviewer is correct that the Reineke is applied to all stems in the stand, in our case the N value is only changing due to the available regeneration at the two diameter thresholds as the adult trees number is the same. By comparing our expected relationship of recruited trees at 7 and 10cm with the Reineke value we are just comparing to a theoretical value in fully stocked stands. We have use the coefficient -1.605 because Reineke attributed a general validity to this allometric coefficient for fully stocked, even-aged forest stands, regardless of tree species and site.

### COMMENT 45

**Response to comment 45:**

### COMMENT 46

L319-321 - overly complex sentence structure

**Response to comment 46:**

We have improved this sentence L\[XX-XX\]

"We tested for significant differences between simulated and observed values of the recruitment levels and species diversity by using paired t-tests."

L323-324 presumably, recruits make up a very small proportion of stand basal if the models have been run to equilibrium?

**Response to comment 47:**

Yes the reviewer is correct, the recruits represent a small proportion of the total stand basal area.

### COMMENT 48

L327 of each species?

**Response to comment 48:**

Added as suggested.

### COMMENT 49

L332-335 This give a matric of species-level variation in recruitment across sites, but how does this relate to the regeneration niche concept of Grubb 1977?

**Response to comment 49:**

We have changed the text to clarify this point. L\[XX-XX\]

"For these species, we calculated the share in the recruited basal area per site, where each site represents a part of the environmental space, as the mean across the available samples per site:"

@@

@@

**Response to comment 50:**

We have changed the text L\[XX-XX\]

@@

**Response to comment 51:**

@@

@@

**Response to comment 53:**

@@

**Response to comment 54:**

@@

**Response to comment 55:**

@@

@@

We have decided not to include this aspect in the abstract due to lack of space.

### COMMENT 57

@@

@@

**Response to comment 59:**

@@

**Response to comment 61:**

@@

**Response to comment 62:**

@@

**Response to comment 63:**

@@

@@

**Response to comment 64:**
